### 2025-08-08 draft.qmd
20250808 - tweaks

```{r}
fantasyPointsByPositionRank <- player_stats_seasonal %>% 
  filter(position_group %in% c("QB","RB","WR","TE","K","DL","LB","DB")) %>% 
  group_by(position_group, season) %>% 
  arrange(position_group, season, -fantasyPoints) %>% 
  mutate(positionRank = row_number())
```

@@

```{r}
#| label: fig-expectedPointsByPositionRank1
#| fig-cap: "Fantasy Points by End-of-Season Position Rank and Position."
#| fig-alt: "Fantasy Points by End-of-Season Position Rank and Position."
#| code-fold: true

ggplot(
  data = fantasyPointsByPositionRank %>% filter(positionRank <= 200),
  mapping = aes(
    x = positionRank,
    y = fantasyPoints
  )
) + 
  geom_point(
    alpha = 0.3
  ) +
  geom_smooth() +
  coord_cartesian(
    ylim = c(0,NA),
    expand = FALSE) + # don't add space between axes and data
  labs(
    x = "End-of-Season Position Rank",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by End-of-Season Position Rank"
  ) +
  theme_bw() +
  facet_wrap(vars(position_group)) # facet by position_group
```

>>>>

```{r}
#| code-fold: true

fantasyPointsByPositionRank <- player_stats_seasonal %>% 
  filter(position_group %in% c("QB","RB","WR","TE","K","DL","LB","DB")) %>% 
  group_by(position_group, season) %>% 
  arrange(position_group, season, -fantasyPoints) %>% 
  mutate(positionRank = row_number())
```

@@

```{r}
#| label: fig-expectedPointsByPositionRank1
#| fig-cap: "Fantasy Points by End-of-Season Position Rank and Position."
#| fig-alt: "Fantasy Points by End-of-Season Position Rank and Position."
#| fig-height: 8
#| code-fold: true

ggplot(
  data = fantasyPointsByPositionRank %>% filter(positionRank <= 200),
  mapping = aes(
    x = positionRank,
    y = fantasyPoints
  )
) + 
  geom_point(
    alpha = 0.03
  ) +
  geom_smooth() +
  coord_cartesian(
    ylim = c(0,NA),
    expand = FALSE) + # don't add space between axes and data
  labs(
    x = "End-of-Season Position Rank",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by End-of-Season Position Rank"
  ) +
  theme_bw() +
  facet_wrap(vars(position_group)) # facet by position_group
```
